Group meetings

### 2023-06-05 diapo/05-06-23_meeting/main.tex
Lowered logos
Changed slides' path

\documentclass[table]{beamer}
\usetheme{gpmeet}

@@

\logo{
  \begin{tikzpicture}[overlay,remember picture]
    \node[left=0cm] at (current page.34){
      \includegraphics[height=1cm]{../figures/ist.eps}
      \hspace{1pt}
      \includegraphics[height=1cm]{figures/inesc-mn.png}
      \includegraphics[height=1cm]{../figures/inesc-id.eps}
    };
  \end{tikzpicture}
}

@@

\begin{frame}
  \frametitle{Introduction}
  \centering\includegraphics[width=\textwidth]{figures/LSTM-NP}
\end{frame}

@@

\begin{frame}{What's new}
  \includegraphics[width=\textwidth]{figures/fulltrial1-all-curves}
\end{frame}

@@

  \centering
  \includegraphics[width=0.7\textwidth]{figures/fulltrial1-memory-prob}
\end{frame}

@@

\begin{frame}{Problems/doubts}
  \centering
  \includegraphics[width=1\textwidth]{figures/fulltrial1-mem-act-late}
\end{frame}

@@

  \centering
  \includegraphics[width=1\textwidth]{figures/fulltrial1-final-res}
\end{frame}

>>>>

\documentclass[table]{beamer}
\usetheme{gpmeet}
\graphicspath{{../../figures/}}

@@

\logo{
  \begin{tikzpicture}[overlay,remember picture]
    \node[below=1pt] at (current page.55){
      \includegraphics[height=1cm]{logos/ist}
      \hspace{1pt}
      \includegraphics[height=1cm]{logos/inesc-mn.png}
      \includegraphics[height=1cm]{logos/inesc-id.eps}
    };
  \end{tikzpicture}
  }

@@

  \begin{frame}
    \frametitle{Introduction}
    \centering\includegraphics[width=\textwidth]{lstm/lstm-np}
  \end{frame}

@@

  \begin{frame}{What's new}
    \includegraphics[width=\textwidth]{fulltrial1/fulltrial1-all-curves}
  \end{frame}

@@

    \centering
    \includegraphics[width=0.7\textwidth]{fulltrial1/fulltrial1-memory-prob}
  \end{frame}

@@

  \begin{frame}{Problems/doubts}
    \centering
    \includegraphics[width=1\textwidth]{fulltrial1/fulltrial1-mem-act-late}
  \end{frame}

@@

    \centering
    \includegraphics[width=1\textwidth]{fulltrial1/fulltrial1-final-res}
  \end{frame}
